\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage{enumitem}
    \usepackage{multicol}
    \usepackage{scrextend}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[margin=.9in]{geometry}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    \usepackage{fontspec} % For loading fonts
    \defaultfontfeatures{Mapping=tex-text}
    \setmainfont{FiraSans-Light}
%    \setmainfont{Carlito} % Calibri-alike

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Henry Zimmerman}}\\
	hgz1374@g.rit.edu $\cdot$ github.com/hgzimmerman $\cdot$ 847-287-1920 \\
\end{center}



%==== Profile ====%
\header{Profile}
    Highly competent Full Stack Web Developer, with experience in languages like \textbf{Java}, \textbf{C\#}, \textbf{Rust}, and \textbf{TypeScript}.
    I have experience working in small teams using both \textbf{Waterfall} and \textbf{Agile} (\textbf{Scrum}, \textbf{Kanban}) software development methodologies.

%==== Education ====%
\header{Education}
    \textbf{BS Software Engineering} \textit{Rochester Institute of Technology}  \hfill  Aug 2019\\
\vspace{2mm}

%==== Experience ====%
\header{Relevant Experience}
\vspace{1mm}

\textbf{Assistant Maintainer (Open Source)}  \hfill April 2018 - Present\\
\textbf{YewStack} \hfill Boston, MA

\begin{addmargin}[1em]{2em}% 1em left, 2em right
    I work directly on \textbf{Yew}, \textbf{Rust}'s largest \textbf{WASM} frontend web framework, contributing numerous bugfixes, added features, documentation and tests.
    As part of my work within the organization, I lead development on the \textbf{Router} implementation, as well as prototyping libraries to add support for \textbf{CSS} and to improve the ergonomics of the framework. 
\vspace*{2mm}

\end{addmargin}




\textbf{Software Engineer (Co-Op)}  \hfill Jan 2018 - May 2018\\
\textbf{MedPoint Digital} \hfill Evanston, IL
\begin{addmargin}[1em]{2em}% 1em left, 2em right
    \textit{{\textbf{JWT Security Audit}}} \\
    Detected that a security flaw in a \textbf{JWT}-based authentication scheme being put in place for a \textbf{C\#/.Net} distributed application which could allow privilege escalation attacks to occur. 
Created documentation demonstrating how exploit and fix the vulnerability in a way that made the system use fewer resources.
\vspace*{2mm}

{\textbf{Uptime Monitoring Tool}} \\ 
Various services for a product had poor reliability and poor visibility for determining when they were unavailable, or if they had been down in the recent past. 
    I wrote an internal tool using \textbf{C\#/ .NET Core} that would record the last three days of uptime for the company's services and displayed those metrics in a webapp written using \textbf{TypeScript} and \textbf{Angular}.
\vspace*{2mm}
\end{addmargin}



\textbf{Software Engineer (Co-Op)}  \hfill Aug 2016 - Jan 2017 \textbar{} May 2017 - Aug 2017\\
\textbf{Ocient} \hfill Chicago, IL

\begin{addmargin}[1em]{2em}% 1em left, 2em right
\textit{\textbf{DB Configuration Client}} \\
I worked on a 2 person team on a webapp that would be used to configure, maintain, and monitor a massively distributed database that was being developed as part of the Ocient’s core product offering.
    I wrote the backend using \textbf{TypeScript} and \textbf{NodeJS} - communicating with the database via \textbf{Protobuf}, as well as the frontend pages using \textbf{Angular} to add features for manipulating clusters and their constituent compute/storage nodes, and for configuring machine learning algorithms to run on those clusters.
\vspace*{2mm}

\textit{\textbf{Performance Monitoring Tool}} \\ 
    Because the database engine development team didn’t have insight into where performance bottlenecks were due to its distributed nature, they instrumented performance counters into their code, exposed them over \textbf{Protobuf}, and tasked me with writing a tool to extract their data. 
    I wrote a Terminal User Interface using \textbf{C++} and \textbf{NCurses} to visualize this data in real time as well as exporting the collected data to \textbf{CSV}, allowing the database team to make informed changes to their code.
\vspace*{2mm}
\end{addmargin}





%\header{Programing Experience}
%\begin{itemize}[leftmargin=*]\itemsep 1pt 
%    \item[]{\makebox[3.2cm][l]{Proficient:} Rust, TypeScript}
%    \item[]{\makebox[3.2cm][l]{Familiar With:} C\#, Java,  Docker, PostgreSQL, React, Angular 2+, WASM, Shell}
%    \item[]{\makebox[3.2cm][l]{Working Knowledge:} JavaScript, Python, MS SQL, C, C++, Android}
%\end{itemize}
%\vspace{2mm}


\header{Team Experience}
\textbf{Rowing Instructor}
Taught sculling to rowing novices of all ages as a Summer job. \hfill 2012 - 2019\\
\vspace*{2mm}

\textbf{RIT Men\textquotesingle{}s Crew}
Rowed and Coxed for RIT\textquotesingle{}s 2nd Varsity 8. \hfill  2014 - 2017\\
\vspace*{2mm}
\end{document}
